### 2019-05-14 manuscript/main.tex
round number SE
add one word to abstract

\begin{abstract}
\onehalfspacing
\noindent
Policy makers generally assume that climate change mitigation requires global scale governance. In contrast, recent studies suggest that polycentrism provides an effective alternative to top-down environmental policies. But despite the high social costs each solution implies, it is unclear which institutional arrangement potential veto players support. Here we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate 6,000 possible climate change agreements. We find that institutional features have a substantial effect on support for climate treaties. Latin American elites prefer multilevel solutions to global warming, but there is considerable heterogeneity across countries and elite types. Our results identify possible challenges in crafting regional climate mitigation agreements, and offer new insights on how to integrate interventions at the local and international levels.

@@

Respondents prefer that international organisations create climate mitigation rules (54\%, SE = 1.2), but they also hold favourable views of local communities (51.6\%, SE = 1.25), local governments (49.8\%, SE = 1.2), and state governments (48.6\%, SE = 1.3) as rule-makers. Although local communities receive slightly more support than the other alternatives, the differences among the three groups are not statistically significant. Interestingly, Latin American elites support multiple levels simultaneously, what suggests they are willing to incorporate separate political spheres into the climate change regime. We also observe that non-governmental organisations are the least preferred option for climate change rule-making with 45.5\% (SE = 1.26).

>>>>

\begin{abstract}
\onehalfspacing
\noindent
Policy makers generally assume that climate change mitigation requires global scale governance. In contrast, recent studies suggest that polycentrism provides an effective alternative to top-down environmental policies. But despite the high social costs each solution implies, it is unclear which institutional arrangement potential veto players support. Here we run a conjoint experiment with elite members of 10 Latin American countries and ask respondents to evaluate 6,000 possible climate change agreements. We find that institutional features have a substantial effect on support for climate treaties. Latin American elites prefer multilevel solutions to tackle global warming, but there is considerable heterogeneity across countries and elite types. Our results identify possible challenges in crafting regional climate mitigation agreements, and offer new insights on how to integrate interventions at the local and international levels.

@@

Respondents prefer that international organisations create climate mitigation rules (54\%, SE = 1.2), but they also hold favourable views of local communities (51.6\%, SE = 1.25), local governments (49.8\%, SE = 1.2), and state governments (48.6\%, SE = 1.3) as rule-makers. Although local communities receive slightly more support than the other alternatives, the differences among the three groups are not statistically significant. Interestingly, Latin American elites support multiple levels simultaneously, what suggests they are willing to incorporate separate political spheres into the climate change regime. We also observe that non-governmental organisations are the least preferred option for climate change rule-making with 45.5\% (SE = 1.3).
